I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-10 Paper/Paper_noProof.tex
Table
Reference

	2. The \emph{Value} of a path is the product of of weights along the path (with sign): for a path $\langle a,b,c,d,e,\cdots\rangle$, its values is $$V = W_{ba}\cdot W_{cb}\cdot W_{dc}\cdot W_{ed}\cdot \cdots$$

@@

		\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

		\textrm{MLP}\ 8$\times$100\  &   0.026& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

		\textrm{MLP}\ 5$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

		\textrm{MLP}\ 8$\times$200\  &   0.015& 1.758 & time & 1.758 & time &    1.758 & time & 1.758 & time \\ \hline

@@

>>>>

	2. The \emph{Value} of a path is the product of of weights along the path (with sign): for a path $\langle a,b,c,d,e,\cdots\rangle$, its values is $$V = W_{ab}\cdot W_{bc}\cdot W_{cd}\cdot W_{ed}\cdot \cdots$$

@@

		\textrm{MLP}\ 5$\times$100\  &   0.026& 1.758 & time & 51 & 159 &    68.4 & 142 & 69.9 & 102 \\ \hline

		\textrm{MLP}\ 8$\times$100\  &   0.026& 52.7 & 92.3 & 42.8 & 301 &    65.8 & 364 & 62 & 103 \\ \hline

		\textrm{MLP}\ 5$\times$200\  &   0.015& 1.758 & time & 69 & 224 &    76.8 & 279 & 77.4 & 86 \\ \hline

		\textrm{MLP}\ 8$\times$200\  &   0.015& 68.1 & 297 & 62.4 & 395 &    79.1 & 535 & 73.5 & 95 \\ \hline

@@

\bibliographystyle{plain}
\bibliography{references}
